---
title: "draft"
format: html
editor: visual
---
git config pull.rebase false

```{r}
library(readr)
college <- read_csv("college.csv")

library(dplyr)
```

##Choice of Topic

##Plan of Work Details

#### Example of is.key
is.key(data, column) or is.key(data$column) or is.key(data, c(column1, column2, ...))
Logic: testing if there are duplicate observations within the listed column(s)
Output: TRUE or FALSE
Requirements: data = dataframe/tibble, no missing values?
Dependencies: Dplyr

# Code for is.key
```{r}
is.key <- function(data, ...) {
  key_candidate <- data |> select(...)
  !any(duplicated(key_candidate))
}

is.key(college, c(stabbr,city))
is.key(college, unitid)
```

#### Example of test.key
test.key(data, column) or test.key(data, column) or test.key(data, c(column1, column2, ...), row = TRUE)
Logic: test for duplicates on only the listed columns, if true count the rows, then do the same for the columns as a key
Output: Summary including columns that are listed in argument with the number of duplicates in each column, plus a "key" output that lists the duplicates for the key
Output: If key = 0 duplicates, a message indicates if that the column combination is a key
Output: If row = TRUE, outputs lists the row numbers that contain duplicates
Requirements: data = dataframe/tibble, no missing values?

# Code for test.key
```{r}
test.ket <- function(data, column_list) {
  
  
}


```

#### Example of find.keys
find.keys(data, n=x)
Output: column a, column b, column c, . . . (for minimum number of columns)
Output: if number of columns to make key = x, return error: no key of this size available

```{r}



```

#### Example of first.normal
first.normal(data)
Output: TRUE/FALSE

```{r}
first.normal <- function(data) {
  if(!any(duplicated(data))) {
    return("FALSE")
  } else {
    
    tryCatch(
      return(find.keys(data)),
      warning = function(w) {
        print("Unable to find key...")
      })
    }
  } 
```




