---
title: "draft"
format: html
editor: visual
---
git config pull.rebase false

```{r}
library(readr)
college <- read_csv("college.csv")

library(dplyr)
```

##Choice of Topic

##Plan of Work Details

#### Example of is.key
is.key(data, column) or is.key(data$column) or is.key(data, c(column1, column2, ...))
Logic: testing if there are duplicate observations within the listed column(s)
Output: TRUE or FALSE, optional argument to show duplicates in each column
Requirements: data = dataframe/tibble, no missing values?
Dependencies: Dplyr

# Code for is.key
```{r}
is.key <- function(data, ..., optional_arguement = FALSE) {
  key_candidate <- data |> select(...)
  !any(duplicated(key_candidate))
}

is.key(college, c(stabbr,city))
is.key(college, unitid)
```


#### Example of find.keys
find.keys(data)
Output: column a, column b, column c, . . . (for minimum number of columns)
Output: if number of columns to make key = x, return error: no key of this size available
Dependency: purrr

```{r}
library(purrr)

find.keys <- function(data) {
  column_names <- colnames(data)
  data |> map_df(function(column_names) {
    for (colname in ncol(data)) {
      if(is.key(colname)) {
        return(print(paste0("Column", colname, "is a key")))
      } else print("hi")
    }
  })
}


find.keys(college)


colnames <- colnames(college)
ncol(college)
  
    
```

#### Example of first.normal
first.normal(data)
Output: TRUE/FALSE

```{r}
first.normal <- function(data) {
  if(!any(duplicated(data))) {
    return("FALSE")
  } else {
    
    tryCatch(
      return(find.keys(data)),
      warning = function(w) {
        print("Unable to find key...")
      })
    }
  } 
```




